\documentclass[10pt,a4paper,ragged2e,withhyper]{altacv}

\geometry{left=1.25cm,right=1.25cm,top=1.5cm,bottom=1.5cm,columnsep=1.2cm}

\usepackage{paracol}

% Color palette
\definecolor{DeepTeal}{HTML}{007377}
\definecolor{DarkNavy}{HTML}{112233}
\definecolor{SoftGrey}{HTML}{4D4D4D}

\colorlet{accent}{DeepTeal}
\colorlet{tagline}{DeepTeal}
\colorlet{heading}{DarkNavy}
\colorlet{headingrule}{DarkNavy}
\colorlet{emphasis}{DarkNavy}
\colorlet{body}{SoftGrey}

\name{Greg Kemp}{}
\tagline{Senior Full-Stack Engineer \textbar{} Systems Architect \textbar{} Product Builder}

\personalinfo{
  \location{Budapest, Hungary}
  \phone{+44 7965 482 696}
  \email{greg@kempgt.com}
  \github{github.com/sgtwickool}
  \linkedin{linkedin.com/in/kempgt}
}

\begin{document}

\makecvheader

\columnratio{0.6}
\begin{paracol}{2}

\cvsection{PROFILE}
I build complete products end-to-end, from database schema to production UI. Originally a mechanical engineer and fusion energy researcher, I bring a first-principles mindset to software. Over 10 years shipping production systems across 6+ greenfield products for brands like Primark and SuperDry. Currently driving a ground-up platform rewrite, replacing a legacy system spanning 10 databases with a modern .NET and Angular stack.

\cvsection{EXPERIENCE}

\cvevent{CORE (UK) Ltd $\rightarrow$ TariffTel}{Trade compliance software for global brands}{Jun 2014 -- Present}{}
Joined as a junior developer. Grew into a senior architect across 6+ greenfield product builds, a company rebrand, and a major platform rewrite, all within a small, high-ownership team.

\medskip
{\color{accent}\textbf{Senior Developer / Architect} \hfill \textit{2022 -- Present}}
\begin{itemize}
  \item Architecting TariffTel 2.0: ground-up rewrite of a 10+ year legacy platform (WebForms, WinForms, millions of lines of SQL across 10 database repos) into .NET 8/10 and Angular 19. Clean Architecture, CQRS, SignalR, Entra ID SSO. Built from scratch in under a year.
  \item Delivered a new Master Data Management System on .NET 10 with a custom CQRS dispatcher and Dapper for performance-critical paths.
  \item Own architectural decisions, mentor developers, and step into the tech lead role when needed.
\end{itemize}

\smallskip
{\color{accent}\textbf{Developer} \hfill \textit{2017 -- 2022}}
\begin{itemize}
  \item Built \textbf{Customs Connect}: customs declaration software for Primark. Rebuilt v2 as a serverless Azure Functions app integrating classification and supply chain data to automate declarations.
  \item Built \textbf{LEAF}: sustainability reporting platform (fibre origin tracking, SCAP scheme). Adopted by Primark; being evaluated by SuperDry before their restructure.
  \item Built \textbf{TariffTel Essentials} (B2C classifier) and later \textbf{TariffTel Premium} (B2B, built single-handedly), which laid the groundwork for the TariffTel 2.0 rewrite.
\end{itemize}

\smallskip
{\color{accent}\textbf{Junior Developer} \hfill \textit{2014 -- 2017}}
\begin{itemize}
  \item Supply chain and classification software for Primark, SuperDry, Triumph Motorcycles. First greenfield project: sustainability reporting for Primark's SCAP fibre-origin programme.
\end{itemize}

\cvsection{SIDE PROJECTS}
\textbf{CodeMop}: AI code review tool (Python/FastAPI/PostgreSQL). Hooks into GitHub PRs and suggests improvements automatically.
\smallskip

\textbf{DevSync}: Multi-tenant snippet manager with team collaboration. Next.js 16, PostgreSQL full-text search, NextAuth, RBAC, Docker.
\smallskip

\textbf{EV Fleet Platform}: .NET 8 fleet API + Python/Flask optimization engine using Google OR-Tools for vehicle routing.

\switchcolumn

\cvsection{WHAT I BRING}
\begin{itemize}
  \item \textbf{Ship complete products}: database to UI, auth to deployment, working solo or in a team.
  \item \textbf{Design systems that last}: Clean Architecture, CQRS, modular boundaries, tested and documented.
  \item \textbf{Pick up anything}: C\#, TypeScript, Python, React, Node. Whatever the problem needs.
  \item \textbf{Move fast, don't cut corners}: Docker, CI/CD, automated tests, and structured logging from day one.
\end{itemize}

\cvsection{TECH}
\cvtag{C\#/.NET}
\cvtag{TypeScript}
\cvtag{Angular}
\cvtag{React}
\cvtag{Python}
\cvtag{Node.js}
\cvtag{SQL Server}
\cvtag{PostgreSQL}
\medskip

\cvtag{Azure}
\cvtag{Docker}
\cvtag{CI/CD}
\cvtag{GitHub Actions}
\medskip

\cvtag{Clean Architecture}
\cvtag{CQRS}
\cvtag{SignalR}
\cvtag{REST APIs}
\cvtag{EF Core}
\cvtag{Dapper}

\cvsection{EDUCATION}

\cvevent{MSc Fusion Energy}{University of York}{2018 -- 2019}{}
\cvevent{BEng Mechanical Eng. (Hons)}{Cardiff University}{2007 -- 2013}{}
\smallskip
{\small Career pivot from engineering to software. I taught myself to code and apply a physicist's rigour to system design.}

\cvsection{LANGUAGES}
\cvskill{English}{5}
\cvskill{Hungarian}{4}
\cvskill{Spanish}{2}

\cvsection{OUTSIDE WORK}
Climbing, mountaineering, caving, outdoor swimming, music (guitar, bass, piano).

\end{paracol}

\end{document}
